Deterministic Scheduling of Periodic Messages in a Network

### 2017-07-06 article/article.tex
codes variance

>>>>

     \begin{algorithm}[H]
    \caption{ Greedy }
    \begin{algorithmic}
    \REQUIRE A routed network $(G,{\cal R})$,a period $P$, packet size $\tau$, $ T_{max}$, the offsets $m_i$
    \ENSURE $(P-\tau)-$periodic assignment of $(G,{\cal R})$, of failure
   \STATE  ${\cal H} \leftarrow$ empty binary min heap
       \STATE  free\_ intervals $\leftarrow$ [0,$P$]

    \FORALL{route $r_{i}$}
    \STATE  deadline[$r_i$]  $\leftarrow$ add $m_{i} + T_{max} - \omega(s_i,c_s)$
    \STATE  eligible\_time[$r_i$] $\leftarrow$ add $m_{i} +  \lambda(r_i) + \omega(c_t,t_i)$
      \ENDFOR

      \WHILE{There is some non-assigned routes}
      \IF{${\cal H}$ is empty}
      \STATE t $\leftarrow $ min\_non\_assigned(eligible\_time)
      \STATE take $r_i$ the route with eligible\_time[$r_i$] = t
      \STATE ${\cal H}$ $\leftarrow$ insert ($r_i$, deadlines($r_i$).
      \ENDIF

      \STATE extract the route $r_i$ with the lowest deadline from ${\cal H}$
      \STATE t $\leftarrow$ beginning of the first free interval of size $\tau$ after t
      \STATE $w_i \leftarrow$ t - eligible\_time[$r_i$]
      \STATE update(free\_ intervals)
      \STATE t $\leftarrow$ t + $\tau$
      \FORALL{routes $r_i$ with  eligible\_time[$r_i$] = t}
      \STATE ${\cal H}$ $\leftarrow$ insert ($r_i$, deadlines($r_i$).
      \ENDFOR
      \ENDWHILE
%    \STATE  $w_i \leftarrow 0$
%    \FORALL{route $r_{t_i}$}
%    \STATE  $w_i \leftarrow 0$
%    \STATE period-end $\leftarrow m_{s_i} + \lambda(r_{s_i}) + t(c_t,r_{t_i}) + P$
%    \FORALL{route $r_{t_j}$}
%    \STATE deadline-route$ \leftarrow m_{s_j} + T_{max}-t(c_s,r_{s_j})$
%    \STATE $deadline \leftarrow$ min(deadline-route,period-end)
%    \ENDFOR

    \end{algorithmic}
    \end{algorithm}
    The function  min\_non\_assigned(eligible\_time) returns the lowest time in eligible\_time, for which the corresponding route is not assigned yet. The function update(free\_ intervals) cuts the interval used in a first part of size $\tau$, which correspond to the message, and a second part with the rest of the size, which is still free.
